acquisition of TEs

### 2020-12-07 Analyze_TEs.Rmd
fixed typo and created an output folder

keepers_ws_TE = keepers_ws_TE %>%
  # keep only necessary variables
  select(-c(vocab_type_dom, vocab_cross_lang, n_administrations)) %>% #n_administrations
  spread(vocab_type, vocab_score) %>%

  ######
  rename(baby_id = Baby_ID, age_months_binned = age.months,
         word_vocab = Totalvocabulary,
         total_words_eng = TotalNW_Eng, total_words_fre = TotalNW_Fr,
         eng_unique_words = Eng_unique_words, fre_unique_words = Fr_unique_words,
         number_of_te = TotalnumberTEs,
         lang_exp_eng = LangExpEng, lang_exp_fre = LangExpFr, lang_exp_other = LangExpOther) %>%

  # calculate age in months (with decimal)
  mutate(age_month_decimal = age_days/30) %>%
  # create balance groups (by exposure)
  mutate(BalanceGroup_byExposure = cut(balance, breaks = 4, 
                                       labels = c("80_20", "70_30", "60_40", "50_50"))) %>%
  mutate(TotalNW_Dom_exposure = case_when(lang_dom == "English" ~ total_words_eng,
                                          lang_dom == "French" ~ total_words_fre),
         TotalNW_NonDom_exposure = case_when(lang_dom == "English" ~ total_words_fre,
                                             lang_dom == "French" ~ total_words_eng),
         Dom_unique_words_exposure = case_when(lang_dom == "French" ~ fre_unique_words, 
                                               lang_dom == "English" ~ eng_unique_words),
         NonDom_unique_words_exposure = case_when(lang_dom == "French" ~ eng_unique_words, 
                                         lang_dom == "English" ~ fre_unique_words)) %>%

@@

# Create dataframe of demographics
d_participants <- keepers_ws_TE %>%
  filter(vocab_type == "word_vocab") %>%
  select(baby_id, age_days, gender, 
         lang_exp_eng, lang_exp_fre, lang_exp_other, years_education) %>%
  mutate(Female = ifelse(gender == "F", 1, 0)) %>%
  summarise(n = n(),
            age.days = mean(age_days, na.rm = TRUE),
            lang_exp_eng = mean(lang_exp_eng, na.rm = TRUE),
            lang_exp_fre = mean(lang_exp_fre, na.rm = TRUE), 
            lang_exp_other = mean(lang_exp_other, na.rm = TRUE),
            years_education = mean(years_education, na.rm = TRUE),
            number_female = sum(Female))
```

## Gender 
```{r}
keepers_ws_TE %>%
  group_by(Gender) %>% 
  distinct(baby_id, .keep.all=T) %>%
  count()
```

@@

do.call(cbind, lapply(keepers_ws_TE %>%
                        distinct(baby_ID, .keep_all = T) %>% 
                        select(age_days,age_continuous),
                      summary))

@@

## average # of TEs
```{r}
keepers_ws_TE %>%
  filter(bothCDI_filled=="Y") %>%
  summarise(mean = mean(propTE, na.rm=T), 
            min= min(propTE, na.rm=T),
            max= max(propTE, na.rm=T))

@@

### Model 1: Predicted_TotalnumberTEs_percentile
Prediction_model <- keepers_ws_TE_simulation %>%
  lm(number_of_te*(Total_90percentile/2) ~ 0 + TotalNW_Dom:TotalNW_NonDom, 
     data = .)

@@

ggsave(here("TEprediction_percentile.png"), TEprediction_percentile)

@@

ggsave(here("TEprediction_percentile&CDI.png"), TEprediction_percentile_CDI)

@@

ggsave(here("TEprediction_percentile&CDI_LessThan100.png"), TEprediction_percentile_CDI_LessThan100)

@@

ggsave(here("TEprediction_percentile&CDI_LessThan50.png"), TEprediction_percentile_CDI_LessThan50)

@@

ggsave(here("TEprediction_percentile&CDI_MoreThan100.png"), TEprediction_percentile_CDI_MoreThan100)

>>>>

keepers_ws_TE = keepers_ws_TE %>%
  # keep only necessary variables
  select(-c(vocab_type_dom, vocab_cross_lang, n_administrations)) %>% #n_administrations
  spread(vocab_type, vocab_score) %>%
  # calculate age in months (with decimal)
  mutate(age_month_decimal = age_days/30) %>%
  # create balance groups (by exposure)
  mutate(BalanceGroup_byExposure = cut(balance, breaks = 4, 
                                       labels = c("80_20", "70_30", "60_40", "50_50"))) %>%
  mutate(TotalNW_Dom_exposure = case_when(lang_dom == "English" ~ total_words_eng,
                                          lang_dom == "French" ~ total_words_fre),
         TotalNW_NonDom_exposure = case_when(lang_dom == "English" ~ total_words_fre,
                                             lang_dom == "French" ~ total_words_eng),
         Dom_unique_words_exposure = case_when(lang_dom == "French" ~ fre_unique_words, 
                                               lang_dom == "English" ~ eng_unique_words),
         NonDom_unique_words_exposure = case_when(lang_dom == "French" ~ eng_unique_words, 
                                         lang_dom == "English" ~ fre_unique_words)) %>%

@@

# Create dataframe of demographics
d_participants <- keepers_ws_TE %>%
  select(baby_id, age_days, gender, 
         lang_exp_eng, lang_exp_fre, lang_exp_other, years_education) %>%
  mutate(Female = ifelse(gender == "F", 1, 0)) %>%
  summarise(n = n(),
            age.days = mean(age_days, na.rm = TRUE),
            lang_exp_eng = mean(lang_exp_eng, na.rm = TRUE),
            lang_exp_fre = mean(lang_exp_fre, na.rm = TRUE), 
            lang_exp_other = mean(lang_exp_other, na.rm = TRUE),
            years_education = mean(years_education, na.rm = TRUE),
            number_female = sum(Female))
```

## Gender 
```{r}
keepers_ws_TE %>%
  group_by(gender) %>% 
  distinct(baby_id, .keep.all=T) %>%
  count()
```

@@

do.call(cbind, lapply(keepers_ws_TE %>%
                        distinct(baby_id, .keep_all = T) %>% 
                        select(age_days,age_continuous),
                      summary))

@@

## average # of TEs
```{r}
keepers_ws_TE %>%
  filter(both_cdi_filled=="Y") %>%
  summarise(mean = mean(propTE, na.rm=T), 
            min= min(propTE, na.rm=T),
            max= max(propTE, na.rm=T))

@@

### Model 1: Predicted_TotalnumberTEs_percentile
Percentile_model <- keepers_ws_TE_simulation %>%
  lm(number_of_te*(Total_90percentile/2) ~ 0 + TotalNW_Dom:TotalNW_NonDom, 
     data = .)

@@

ggsave(here("Output/TEprediction_percentile.png"), TEprediction_percentile)

@@

ggsave(here("Output/TEprediction_percentile&CDI.png"), TEprediction_percentile_CDI)

@@

ggsave(here("Output/TEprediction_percentile&CDI_LessThan100.png"), TEprediction_percentile_CDI_LessThan100)

@@

ggsave(here("Output/TEprediction_percentile&CDI_LessThan50.png"), TEprediction_percentile_CDI_LessThan50)

@@

ggsave(here("Output/TEprediction_percentile&CDI_MoreThan100.png"), TEprediction_percentile_CDI_MoreThan100)
